### 2012-10-16 papers/tevcat/tables.tex
fixed the bibtex

\tablecomments{This table summarizes the pulsars properties taken into account in this analysis to perform the populations studies in Figures \ref{fig:dotelpwn} \& \ref{fig:rapportX}. Column 3 shows the pulsar spin-down power as found in the litterature, column 4 and 5 present the characteristic age of the pulsar and its distance.\\References: (1) \cite{1973PASP...85..579T}, (2) \cite{2008MNRAS.389.1881K}, (3) \cite{2004MNRAS.352.1405C}, (4) \cite{dalton1303}, (5) \cite{2005yCat.7245....0M}, (6) \cite{2006MNRAS.372..777L}, (7) \cite{1997ApJ...476..347Y}, (8) \cite{2012ApJ...750..162K}, (9) \cite{2009ApJ...694...12M}, (10) \cite{1996ApJ...471..887S}, (11) \cite{1999ApJ...511..274S}, (12) \cite{2007ApJ...662..517F}, (13) \cite{2003MNRAS.342.1299K}, (14) \cite{1995A&A...293..795J},  (15) \cite{2001MNRAS.328...17M}, (16) \cite{2011ICRC....7..247H}, (17) \cite{2006ApJ...637..456C}, (18) \cite{2012ApJ...755L..20P}, (19) \cite{2008AIPC.1085..372C}, (20) \cite{2011ApJ...729L..16G}, (21) \cite{2010ApJ...708.1426W}, (22) \cite{2012ApJ...755...39V}, (23) \cite{1997ApJ...476..347Y}, (24) \cite{2004ApJ...612..389H}, (25) \cite{2009ApJ...706.1331A}, (26) \cite{2001ApJ...560..236K}, (27) \cite{1993AJ....105.1060P}, (28) \cite{2008AJ....136.1477L}, (29) \cite{2003ApJ...596.1137D}, (30) \cite{2010ApJ...725..571S}, (31) \cite{2009ApJ...691..895T}, (32) \cite{2010A&A...520A.111B}.}

@@

\tablecomments{This table summarizes the PWNe properties and the fluxes taken into account in this analysis to perform the populations studies in Figures \ref{fig:dotelpwn} \& \ref{fig:rapportX}. Column 2,3 and 4 summarize the fluxes found in the GeV (10-316 GeV) , TeV (1-30 TeV) and X-ray (2-10 keV) energy ranges. Column 5 shows the luminosity found using the energy flux in column 2 and the distance in Table \ref{tab:table_luminosity}. \\References : (1) \cite{2009ApJ...694...12M} and references therein, (2) \cite{2011AA...525A..46H}, (3) \cite{Mayerdiploma}, (4) \cite{2011AA...533A.103H}, (5) \cite{2012arXiv1205.0719D}, (6) \cite{2010A&A...520A.111B}, (7) \cite{2006ApJ...636..777A}, (8) \cite{2011arXiv1112.2901H}, (9) \cite{2008AA...477..353A}, (10) \cite{2008AIPC.1085..372C}, (11) \cite{2008AIPC.1085..312T}, (12) \cite{dalton1303}, (13) \cite{2012ApJ...750..162K}, (14) \cite{2009ApJ...691..895T}.}

>>>>

\tablecomments{This table summarizes the pulsars properties taken into account in this analysis to perform the populations studies in Figures \ref{fig:dotelpwn} \& \ref{fig:rapportX}. Column 3 shows the pulsar spin-down power as found in the litterature, column 4 and 5 present the characteristic age of the pulsar and its distance.\\References: (1) \cite{1973PASP...85..579T}, (2) \cite{2008MNRAS.389.1881K}, (3) \cite{2004MNRAS.352.1405C}, (4) \cite{dalton1303}, (5) \cite{2005yCat.7245....0M}, (6) \cite{2006MNRAS.372..777L}, (7) \cite{1997ApJ...476..347Y}, (8) \cite{2012ApJ...750..162K}, (9) \cite{2009ApJ...694...12M}, (10) \cite{1996ApJ...471..887S}, (11) \cite{1999ApJ...511..274S}, (12) \cite{2007ApJ...662..517F}, (13) \cite{2003MNRAS.342.1299K}, (14) \cite{1995AA...293..795J},  (15) \cite{2001MNRAS.328...17M}, (16) \cite{2011ICRC....7..247H}, (17) \cite{2006ApJ...637..456C}, (18) \cite{2012ApJ...755L..20P}, (19) \cite{2008AIPC.1085..372C}, (20) \cite{2011ApJ...729L..16G}, (21) \cite{2010ApJ...708.1426W}, (22) \cite{2012ApJ...755...39V}, (23) \cite{1997ApJ...476..347Y}, (24) \cite{2004ApJ...612..389H}, (25) \cite{2009ApJ...706.1331A}, (26) \cite{2001ApJ...560..236K}, (27) \cite{1993AJ....105.1060P}, (28) \cite{2008AJ....136.1477L}, (29) \cite{2003ApJ...596.1137D}, (30) \cite{2010ApJ...725..571S}, (31) \cite{2009ApJ...691..895T}, (32) \cite{2010AA...520A.111B}.}

@@

\tablecomments{This table summarizes the PWNe properties and the fluxes taken into account in this analysis to perform the populations studies in Figures \ref{fig:dotelpwn} \& \ref{fig:rapportX}. Column 2,3 and 4 summarize the fluxes found in the GeV (10-316 GeV) , TeV (1-30 TeV) and X-ray (2-10 keV) energy ranges. Column 5 shows the luminosity found using the energy flux in column 2 and the distance in Table \ref{tab:table_luminosity}. \\References : (1) \cite{2009ApJ...694...12M} and references therein, (2) \cite{2011AA...525A..46H}, (3) \cite{Mayerdiploma}, (4) \cite{2011AA...533A.103H}, (5) \cite{2012arXiv1205.0719D}, (6) \cite{2010AA...520A.111B}, (7) \cite{2006ApJ...636..777A}, (8) \cite{2011arXiv1112.2901H}, (9) \cite{2008AA...477..353A}, (10) \cite{2008AIPC.1085..372C}, (11) \cite{2008AIPC.1085..312T}, (12) \cite{dalton1303}, (13) \cite{2012ApJ...750..162K}, (14) \cite{2009ApJ...691..895T}.}
